\documentclass{article}
\usepackage{gensymb, amsmath, float, graphicx, epstopdf}
\restylefloat{table}
\usepackage[margin=0.75in]{geometry}
\usepackage{multicol}
\begin{document}

\title{Lab Write-up 6: Impedance Matching and Frequency Tuning}
\author{Michael Shen}
\date{December 15, 2014}
\maketitle


\section{Testing the Matching Networks}

\subsection{Measured Data}
As measured in the previous lab and confirmed in this lab, $\omega_{0_{9cm}} = 46.973$ MHz.

\begin{enumerate}
	\item Measured output impedance for loop matching network \#1: 14.40 - j20.23 $\Omega$
	\item Measured output impedance for loop matching network \#2: 15.26 - j20.21 $\Omega$
	\item Measured output impedance for rectifier matching network: 2.312 - j30.54 $\Omega$
	\item Input return loss of matched rectifier: -21.904 dB
	\item Input return loss of matched system at 10cm: -26.527 dB
\end{enumerate}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|}
\hline
Distance (cm) & Input Return Loss (dB) \\ \hline
2             & -0.702                 \\ \hline
4             & -1.880                 \\ \hline
6             & -5.117                 \\ \hline
8             & -10.631                \\ \hline
10            & -26.527                \\ \hline
12            & -10.627                \\ \hline
14            & -6.917                 \\ \hline
16            & -3.712                 \\ \hline
\end{tabular}
\end{table}

\subsection{Questions}

\begin{enumerate}
	\item Why shouldn't we use a length of cable between the matching networks and the loops or the rectifier and its matching network? Why doesn't it matter whether we have a length of line between the matched rectifier and the matched loops?

\end{enumerate}


\section{Frequency-Tuned System}

\subsection{Measured Data}
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
Distance (cm) & Odd Mode Frequency (MHz) & Even Mode Frequency (MHz) \\ \hline
2             & 40.501                   & 63.172                    \\ \hline
4             & 43.372                   & 55.549                    \\ \hline
6             & 45.286                   & 53.008                    \\ \hline
8             & 46.474                   & 51.358                    \\ \hline
10            & 47.893                   & 49.672                    \\ \hline
12            & 48.817                   & 48.817                    \\ \hline
14            & 48.817                   & 48.817                    \\ \hline
16            & 48.817                   & 48.817                    \\ \hline
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|}
\hline
Distance (cm) & Constant Frequency $\vert S_{21}\vert$ (dB) 
& Frequency-Tuned $\vert S_{21}\vert$ (dB) \\ \hline
2             & -7.767                          & -0.621                       \\ \hline
4             & -4.622                          & -0.558                       \\ \hline
6             & -2.630                          & -0.663                       \\ \hline
8             & -1.176                          & -0.733                       \\ \hline
10            & -0.593                          & -0.743                       \\ \hline
12            & -0.938                          & -0.938                       \\ \hline
14            & -1.904                          & -1.904                       \\ \hline
16            & -3.360                          & -3.360                       \\ \hline
\end{tabular}
\end{table}

\subsection{Analysis}

\begin{enumerate}
	\item Using (6.33) determine the theoretical power transfer efficiency from 2-16cm
	\item Using (6.39) determine the theoretical power transfer efficiency at the odd mode frequency from 2-16cm
	\item Using (6.37) and circuit values plot the maximum power transfer efficiency from 2-16cm
\end{enumerate}

\subsection{Questions}

\begin{enumerate}
	\item How does the input reflection coefficient of the matched system behave as the loops are moved away from the matching distance?
	\item Plot the theoretical efficiency and matched efficiency on the same axis, compare.
	\item Does the coupling distance with minimum return loss correspond to the coupling distance with Maximum S21 for the constant omega0 system?
	\item Plot the theoretical efficiency vs measured efficiency for the frequency-tuned system, compare.
	\item Why is the critical coupling distance different.
\end{enumerate}

\section{Summary}

\end{document}